sims

### 2025-06-14 sims/sims.Rmd
Improve Figure 1 details

```{r}
p13.1 <-ggplot(lifetable_fig1, aes(x = bin, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits = c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
 # ggtitle("hazard and conditional accuracy functions") +
  xlab("time bin endpoint") +
  theme(axis.text.x = element_text(angle = 90))
p13.1

@@

```{r}
p13.2 <-ggplot(ca, aes(x = bin, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits=c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin endpoint") +
    ylab("conditional accuracy") +
   theme(axis.text.x = element_text(angle = 90))

@@

```{r}
p13.5 <- ggplot(acc_dat_fig1_pid, aes(x = condition, y = mean, fill=condition, color=condition)) +
  geom_col(alpha = 0.9, width = 0.6) +
  geom_errorbar(
    aes(ymin = mean - sem, ymax = mean + sem),
    width = 0.2,
    linewidth = 0.8,
    color = "black"
  ) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
 #  ggtitle("mean accuracy by condition") +
   scale_y_continuous(limits = c(0, 1)) +
   ylab("accuracy")
p13.5
```

@@

```{r}
p13.6 <- (p13.4 / p13.5) +
  plot_layout(guides = 'collect',
              axes = 'collect')
p13.6

plot_grid(p13.6, p13.3,
  nrow = 1,
  labels = c("A","B"),
  label_size = 22
)

>>>>

```{r}
p13.1 <-ggplot(lifetable_fig1, aes(x = bin, y = hazard,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits = c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
 # ggtitle("hazard and conditional accuracy functions") +
  xlab("time bin endpoint (ms)") +
  ylab("hazard") +
  theme(axis.text.x = element_text(angle = 90),
        panel.grid.minor.x = element_blank()) +
  annotate("label", x = 2, y = .95,
           label = "h(t) = P(RT = t | RT ≥ t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)
p13.1

@@

```{r}
p13.2 <-ggplot(ca, aes(x = bin, y = ca,
                         colour = condition)) +
  geom_line(linewidth = 1) +
  geom_point(size=3) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_colour_brewer(palette = "Dark2") + 
  scale_x_continuous(breaks = 1:10, limits=c(1,10),labels = c(1:10)*100) +
  scale_y_continuous(limits = c(0,1)) +
  xlab("time bin endpoint (ms)") +
    ylab("conditional accuracy") +
   theme(axis.text.x = element_text(angle = 90),
         panel.grid.minor.x = element_blank()) +
   annotate("label", x = 2, y = .25,
           label = "ca(t) = P(correct | RT = t)",
           fill = "white",           # White background
           color = "black", 
           size = 7, 
           hjust = 0)

@@

```{r}
p13.5 <- ggplot(acc_dat_fig1_pid, aes(x = condition, y = mean, fill=condition, color=condition)) +
  geom_col(alpha = 0.9, width = 0.6) +
  geom_errorbar(
    aes(ymin = mean - sem, ymax = mean + sem),
    width = 0.2,
    linewidth = 0.8,
    color = "black"
  ) +
   scale_fill_brewer(palette = "Dark2") +
   scale_colour_brewer(palette = "Dark2") +
 #  ggtitle("mean accuracy by condition") +
   scale_y_continuous(limits = c(0, 1)) +
   ylab("mean accuracy (%)")
p13.5
```

@@

```{r}
p13.6 <- (p13.4 / p13.5) +
  plot_layout(guides = 'collect',
              axes = 'collect')
p13.6
```

Plot mean and distributional results:

```{r}
plot_grid(p13.6, p13.3,
  nrow = 1,
  labels = c("A","B"),
  label_size = 22
)
```
